\chapter{Introduction}

The website of RZZT CIC has developed and grown significantly since the current framework was launched in February 2018.

A website can fulfil many purposes. In broad terms, a website for an organisation like RZZT is intended to provide information about the organisation and its activities to a general audience. However, because the Company places an emphasis on transparency, a significant number of records are published via the website.

The website is a static website that is compiled using Jekyll. Jekyll is an exceptionally versatile Ruby-based platform for creating websites. Although it has usually been used as a framework for blogging, it has enormous potential for processing other types of data, and can be used to create sophisticated static websites.

The source files for the website are hosted by GitHub, which Netlify accesses to recompile and serve the website automatically when changes are made.

As a result of the policy of transparency and the power of Jekyll to process different sorts of data, the website has become not merely a way of presenting information, but of storing and processing it too.

The source files for the website include files that generate `normal' content --- pages, blog posts, press releases and announcements. However, they also include files that generate accounting records, minutes of meetings and decisions, structural documents, and even a timeline function. The website not only publishes this information, it \textit{generates it}. The accounts, for example, are entirely generated using Jekyll.

This book, with the invigorating title `RZZT CIC Website Documentation', covers all the custom functionality that has been incoporated to make such a website possible, and increase the bus factor beyond one.

\vspace{1em}

\hspace{0.5\textwidth}\noindent Mozart Olbrycht-Palmer

\hspace{0.5\textwidth}\noindent Director \& Company Secretary

\hspace{0.5\textwidth}\noindent \today
