\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
  \setmainfont{Open Sans}
\usepackage{parskip}
  \setlength{\parskip}{1em}
\usepackage{titlesec}
  \titleformat{\section}{\raggedright\LARGE\bfseries}{}{0em}{}[\hrule]
  \titlespacing{\section}{0em}{1em}{2em}
  \titleformat{\subsection}{\raggedright\Large\bfseries}{}{0em}{}[\hrule]
  \titlespacing{\subsection}{0em}{1em}{1em}
  \titleformat{\subsubsection}{\raggedright\bfseries}{}{0em}{}
  \titlespacing{\subsubsection}{0em}{0em}{0em}
\usepackage{xcolor}
\usepackage{framed}
  \FrameSep0.5em
  \usepackage{fancyhdr}
  	\lhead{RZZT CIC}
  	\chead{}
  	\rhead{Financial arrangements discussion paper \#1}
    \lfoot{\thepage}
    \rfoot{2017-09-22}
    \cfoot{}
  	\renewcommand{\headrule}{}
  	\pagestyle{fancy}
    \fancypagestyle{firstpage}{%
      \lhead{}
      \rhead{}
      \lfoot{\thepage}
      \rfoot{2017-09-22}
    }
    \usepackage{adjustbox}
    \usepackage{array}

    \newcolumntype{R}[2]{%
        >{\adjustbox{angle=#1,lap=\width-(#2)}\bgroup}%
        l%
        <{\egroup}%
    }
    \newcommand*\rot{\multicolumn{1}{R{45}{1em}}}% no optional argument here, please!
\usepackage{draftwatermark}

\begin{document}

\thispagestyle{firstpage}

\raggedright

\section{RZZT CIC}

UK company number 10951485

\section{Financial arrangements proposal paper \#1}

\subsection{Executive summary}

It is proposed that RZZT have the following financial arrangements to receive contributions from the public:

\begin{itemize}
\setlength\itemsep{-0.5em}
\item Credit and debit cards should be handled exclusively via Stripe, which will deposit funds directly into a nominated bank account.
\item PayPal should be handled via Braintree, which will deposite funds into a nominated PayPal account, from which funds should be transferred to a nominated bank account at least once every 48 hours.
\item Patreon be used sparingly due to the high fees associated with receiving contributions.
\item Direct deposit should be offered to a nominated bank account.
\item Cheques and cash should not be accepted.
\item Cryptocurrencies should not be accepted for the time being.
\end{itemize}

\subsection{Credit and debit cards}

Payment gateways can be used to deposit funds directly into the nominated bank account from contributors paying with credit and debit cards. Stripe and Braintree (a PayPal subsidiary) charge fees on a per-transaction basis. At the time of writing, both Stripe and Braintree support recurring payments, but only Stripe appears to support pay-what-you-want contributions. The following table compares Stripe and Braintree's fees in GBP, USD and AUD for domestic (`dom') and international (`int') cards (note that `domestic' includes European cards in the case of GBP, and American Express cards may be subject to higher rates).

\begin{center}
{\renewcommand{\arraystretch}{1.5}%
\begin{tabular}{r | c | c | c }
                & GBP            & USD             & AUD             \\ \hline
Braintree (dom) & 1.90\% + £0.20 & 2.90\% + \$0.30 & 1.75\% + \$0.30 \\
Braintree (int) & 2.90\% + £0.20 & 3.90\% + \$0.30 & 3.90\% + \$0.30 \\
Stripe (dom)    & 1.40\% + £0.20 & 2.90\% + \$0.30 & 1.75\% + \$0.30 \\
Strip (int)     & 2.90\% + £0.20 & 3.90\% + \$0.30 & 2.90\% + \$0.30
\end{tabular}}
\end{center}

\subsection{PayPal}

It is generally desirable to avoid using PayPal, due to its practice of seemingly arbitrarily freezing accounts. However, it is a necessary evil in order to maximise revenue sources. While it should be offered, financial contributors should be directed towards alternatives as much as possible. Braintree provides a convenient API to handle PayPal (in addition to credit and debit cards as above), which can be integrated with RZZT's own branding. PayPal offers quite poor rates for transaction fees: for example, RZZT would likely be paying 3.4\% + £0.20 on most transactions, on top of currency conversion fees that may apply. Money paid into the PayPal account should be held only temporarily, and transfers from the Company's PayPal account to its bank account should be initiated at least once every 48 hours. PayPal should not be used for long-term storage of funds, or for storing large sums of money.

\subsection{Patreon}

Patreon combines pay-what-you-want payments (according to predefined amounts set by the recipient) with monthly subscriptions and the ability to offer rewards. The fees are \$3 \textit{per} transfer from Patreon to a non-US bank account (or \$0.25 if deposited to a US bank account which, incidentally, uses Stripe), or 1\% of the amount transferred (capped at \$20), on top of the 5\% it already takes from payments. Funds can be accumulated before being transferred from Patreon to a bank account to minimise transaction fees.

\subsection{Direct deposits}

Direct deposit between domestic bank accounts and international transfers via the SWIFT network can be done easily by publishing the required details provided by the Company's financial institution on the Company's website, or at request, depending on the specific requirements. Bank transfers do not require funds to be held in an intermediary account.

\subsection{Cheques and cash}

Cheques and cash are cumbersome, impractical and inefficient in the case of RZZT. They should not be accepted due to the potential costs and difficulties in depositing them.

\subsection{Cryptocurrencies}

Receiving payments in cryptocurrencies is potentially possible. However, there remains significant legal uncertainty, and an associated administrative and regulatory burden. For the time being, RZZT should not deal in cryptocurrencies, but this may change at a later stage.

\end{document}
